The SMT Competition 2015--2018

### 2019-03-19 2018/report/SMT-COMP.tex
New layout for winners table (currently only main).
Beautify layout of main track winners table.
Removed old main track winners table.
New layout for application winners table.

\documentclass[twoside,11pt]{article}

@@

@@

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[4ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{Virtual Best Solver (VBS) on common benchmarks of all
  logics in the Main track.}
  \label{fig:progress}
\end{figure}

>>>>

\documentclass[dvipsnames,table,twoside,11pt]{article}

@@

\newcommand{\nc}[1]{{[}#1{]}}
\newcommand{\cc}{\cellcolor{white}}
\newcommand{\rc}{\rowcolor{white}}
\newcommand{\drc}{\rowcolor[gray]{.9}}
\newcommand{\dcc}{\cellcolor[gray]{.9}}

@@

\begin{figure}
  \centering
  \scalebox{.45}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2018.pdf}}
  \caption{VBS on common benchmarks 2015-2018 of all logics in the Main track.}
  \label{fig:progress-all}
\end{figure}

\begin{figure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
        plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2014-2015.pdf}}
    \caption{2014 vs.~2015}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2015-2016.pdf}}
    \caption{2015 vs.~2016}
  \end{subfigure}
  \\[2ex]
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
      plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2016-2017.pdf}}
    \caption{2016 vs.~2017}
  \end{subfigure}
  \begin{subfigure}[t]{0.5\textwidth}
    \scalebox{.35}{\includegraphics{%
    plot/pdf/cactus_plot-Virtual_Best_Solver_(VBS)_2017-2018.pdf}}
    \caption{2017 vs.~2018}
  \end{subfigure}
  \caption{VBS on common benchmarks for pairs of years of all logics in the
  Main track.}
  \label{fig:progress}
\end{figure}

### 2019-03-19 2018/report/table-winners-main.tex
New layout for application winners table.

  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}

@@

\cc ALIA         & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\

@@

\cc AUFLIRA      & \cc CVC4 {{[}Z3{]}}      & Vampire {{[}Z3{]}}      & Vampire {{[}Z3{]}}             & \cc CVC4 {{[}Z3{]}}            \\

@@

\cc BV           & \cc CVC4 {{[}Z3{]}} *    & {Q3B}           & Q3B {{[}Z3{]}}             &  \cc {CVC4}               \\

@@

\cc LIA          & {CVC4}     & {CVC4}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc LRA          & {CVC4}     & {CVC4}     & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc NIA          & \cc CVC4 {{[}Z3{]}} *     & \cc ProB {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\

@@

\cc NRA          & {CVC4} *        & {Vampire}       & {Redlog}               & Vampire {{[}Z3{]}/Vampire}    \\

@@

\cc QF\_ANIA     & CVC4 {{[}Z3{]}} *& {CVC4} *        & {CVC4} *               & CVC4 {{[}Z3{]}} *           \\
\cc QF\_AUFBV    & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & Yices2 {{[}MathSAT{]}}        & \cc {CVC4}            \\

@@

\cc QF\_AUFNIA   & {CVC4} *        & {CVC4} *        & CVC4 {{[}Z3{]}} *        & CVC4 {{[}Z3{]}} *     \\

@@

\cc QF\_BV       & {Boolector}     & {Boolector}     & {Boolector/MinkeyRink}   & {Boolector/MinkeyRink}\\
\cc QF\_BVFP     & {Z3} *          & {{[}Z3{]}} *    & \cc COLIBRI {{[}Z3{]}} * & \cc {CVC4}            \\

@@

\cc QF\_FP       & \cc {Z3} *      & \cc {{[}MathSAT{]}} * & COLIBRI {{[}Z3{]}}             & {COLIBRI}             \\

@@

\cc QF\_IDL      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\
\cc QF\_LIA      & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}} & CVC4 {{[}MathSAT{]}}        & \cc {SPASS-SATT}      \\

@@

\cc QF\_LIRA     & {Yices2}        & {Yices2}        & Yices2 {{[}Z3{]}}        & Yices2 {{[}Z3{]}}       \\

@@

\cc QF\_NIA      & \cc AProVE {{[}Z3{]}} & \cc Yices2 {{[}Z3{]}} & {CVC4}                 & {CVC4}                \\

@@

\cc QF\_NRA      & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}}      & {Yices2}      & Yices2 {{[}Z3{]}}        \\

@@

\cc QF\_UFLIA    & Yices2 {{[}Z3{]}} & Yices2 {{[}Z3{]}} & {Yices2}               & {Yices2}              \\

@@

\cc QF\_UFNRA    & \cc CVC3 {{[}Z3{]}} *     & {Yices2}        & Yices2 {{[}Z3{]}}             & {Yices2}              \\

@@

\cc UFBV         & CVC4 {{[}Z3{]}} *    & CVC4 {{[}Z3{]}}      & CVC4 {{[}Z3{]}} *            & CVC4 {{[}Z3{]}} *           \\

@@

\cc UFIDL        & CVC4 {{[}Z3{]}}  & {CVC4}          & {CVC4}                 & CVC4 {{[}Z3{]}}        \\

@@

\cc UFLRA        & \cc {CVC3}      & \cc Vampire {{[}Z3{]}}      & CVC4 {{[}Z3{]}}             & CVC4 {{[}Z3{]}}            \\
\cc UFNIA        & \cc {CVC4} *    & {Vampire}       & {Vampire}              & Vampire {{[}Z3{]}/Vampire}    \\

>>>>

  \begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.5em]}c}

@@

    \cc ALIA         & CVC4 \nc{Z3}       & CVC4 \nc{Z3}        & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\

@@

    \cc AUFLIRA      & \cc CVC4 \nc{Z3}   & Vampire \nc{Z3}     & Vampire \nc{Z3}       & \cc CVC4 \nc{Z3}        \\

@@

    \cc BV           & \cc CVC4 \nc{Z3} * & {Q3B}               & Q3B \nc{Z3}           &  \cc {CVC4}             \\

@@

    \cc LIA          & {CVC4}             & {CVC4}              & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
    \cc LRA          & {CVC4}             & {CVC4}              & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
    \cc NIA          & \cc CVC4 \nc{Z3} * & \cc ProB \nc{Z3}    & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\

@@

    \cc NRA          & {CVC4} *           & {Vampire}           & {Redlog}              & Vampire \nc{Z3/Vampire} \\

@@

    \cc QF\_ANIA     & CVC4 \nc{Z3} *     & {CVC4} *            & {CVC4} *              & CVC4 \nc{Z3} *          \\
    \cc QF\_AUFBV    & CVC4 \nc{MathSAT}  & CVC4 \nc{MathSAT}   & Yices2 \nc{MathSAT}   & \cc {CVC4}              \\

@@

    \cc QF\_AUFNIA   & {CVC4} *           & {CVC4} *            & CVC4 \nc{Z3} *        & CVC4 \nc{Z3} *          \\

@@

    \cc QF\_BV       & {Boolector}        & {Boolector}         & {Boolector/MinkeyRink}& {Boolector/MinkeyRink}  \\
    \cc QF\_BVFP     & {Z3} *             & \nc{Z3} *           & \cc COLIBRI \nc{Z3} * & \cc {CVC4}              \\

@@

    \cc QF\_FP       & \cc {Z3} *         & \cc \nc{MathSAT} *  & COLIBRI \nc{Z3}       & {COLIBRI}               \\

@@

    \cc QF\_IDL      & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & {Yices2}                \\
    \cc QF\_LIA      & CVC4 \nc{MathSAT}  & CVC4 \nc{MathSAT}   & CVC4 \nc{MathSAT}     & \cc {SPASS-SATT}        \\

@@

    \cc QF\_LIRA     & {Yices2}           & {Yices2}            & Yices2 \nc{Z3}        & Yices2 \nc{Z3}          \\

@@

    \cc QF\_NIA      & \cc AProVE \nc{Z3} & \cc Yices2 \nc{Z3}  & {CVC4}                & {CVC4}                  \\

@@

    \cc QF\_NRA      & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & Yices2 \nc{Z3}          \\

@@

    \cc QF\_UFLIA    & Yices2 \nc{Z3}     & Yices2 \nc{Z3}      & {Yices2}              & {Yices2}                \\

@@

    \cc QF\_UFNRA    & \cc CVC3 \nc{Z3} * & {Yices2}            & Yices2 \nc{Z3}        & {Yices2}                \\

@@

    \cc UFBV         & CVC4 \nc{Z3} *     & CVC4 \nc{Z3}        & CVC4 \nc{Z3} *        & CVC4 \nc{Z3} *          \\

@@

    \cc UFIDL        & CVC4 \nc{Z3}       & {CVC4}              & {CVC4}                & CVC4 \nc{Z3}            \\

@@

    \cc UFLRA        & \cc {CVC3}         & \cc Vampire \nc{Z3} & CVC4 \nc{Z3}          & CVC4 \nc{Z3}            \\
    \cc UFNIA        & \cc {CVC4} *       & {Vampire}           & {Vampire}             & Vampire \nc{Z3/Vampire} \\
